---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cvera

<!-- badges: start -->
<!-- badges: end -->

---

`cvera` is an R package with a collection of utility R functions that can be useful to explore Irish bTB datasets collated in CVERA.

---

## Installation

You can install the development version of cvera from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("044mj/cvera")
```

## Example

Extract yearly summary data and visualisations of reactor numbers from `master_tb` dataset. 

Read in data:

```{r reading_in, include = T, warning = FALSE, eval = FALSE}
library(tidyverse)
# if using readr::read_csv() they use first 1000 rows to guess type. 
# If the first 1,000 are missing, it will default to logical. GIF variables are missing in the first 1000
#because it only came in during May 2019 so include col_types for these variables:
master_tb <- read_csv("N:/data/tb/master_tb_data_jamie_m/year_2022/master_tb_15_Mar_2022.csv", 
                          col_types = cols(.default = "?", 
                                           gif8d_actual_date = col_date(), 
                                           gif_cases = col_number()))
```

Using `all_cases_per_year` from `cvera` package:

```{r example, eval = FALSE}
library(cvera)
#drop 2022 figures as we only have 3 months worth of data
cases <- all_cases_per_year(master_tb, drop_years = c(2022))
```


results in










